Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-04-24 eg6-letters/long-paper/prc-dvcshelium.tex
Add pi0 contamination figures.

The $\pi^0$ contamination was found to be 2 to 4\% in the coherent channel and 3 to 17\% in the incoherent
channel (with variations between kinematic bins). To make the correction on the DVCS BSA, we assume that
the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
$\pi^0$ production data, for which no significant level of BSA has been measured.

@@

\begin{figure}[bp!]
\center
\includegraphics[width=12cm]{fig3/Coherent_ALU_phi.pdf}
	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
	function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
	statistical, Grey bands represent the systematic uncertainties. The full red lines show
	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
	%TODO Add the chi2 somewhere
\label{fig:CohALUphi}
\end{figure}

@@

%TODO add sentence on recent theory and one on ALERT

\begin{acknowledgments}
The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University. M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
\end{acknowledgments}

@@

\section{Table of results with kinematic information}
\label{sec:fullresults}

>>>>

We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ bins, where it varies
the most from one bin to another. The study
shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
channel. To make the correction on the DVCS BSA, we assume that
the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
$\pi^0$ production data, for which no significant level of BSA was measured.

\begin{figure}[tbp]
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
contamination estimated in the DVCS events as a function of the 
transfered momentum squared -$t$ and integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.}
\label{fig:cont_yield}
\end{figure}

@@

\begin{figure}[bp!]
\center
\includegraphics[width=12cm]{fig3/Coherent_ALU_phi.pdf}
	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
	function of $\phi$ and $Q^2$ 
	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
	statistical, Grey bands represent the systematic uncertainties. The full red lines show
	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
\label{fig:CohALUphi}
\end{figure}

@@

\begin{acknowledgments}
The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University. M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem. This work has received funding from 
the European Research Council (ERC) under the European Union’s Horizon 2020 
research and innovation programme (Grant agreement No. 804480). The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
\end{acknowledgments}

@@

\section{Table of results with kinematic information}
\label{sec:fullresults}
%TODO Tables to be checked
